---
output: rmarkdown::github_document
---

`databox` : Tools to work with the ['databox' 'API'](https://databox.com/)

The following functions are implemented:

- `add_metric`:	Add a metric to send to databox
- `client`:	Initialize a databox client and return a databox client object (dco)
- `databox_api_key`:	Get or set `DATABOX_API_KEY` value
- `last_push`:	Retrieve the metrics posted in the past push
- `push`:	Push metrics to databox

The following data sets are included:

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/databox")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE}
library(databox)
library(dplyr)

# current verison
packageVersion("databox")
```

We can send one or more metrics to databox. They can be combined in a pipe as well. Once they're "pushed" they are cleared from the client object:

```{r}
databox::client() %>% 
  add_metric("sales", 83000, Sys.Date()) %>% 
  add_metric("sales", 4000, unit="USD") %>% 
  add_metric("expenses", 87500) %>% 
  add_metric("sales", 123000, mattrs=c("channel"="in-person", "cheese"="manchego")) %>% 
  push()
```

There's a `print()` method for `dco` objects as well:

```{r}
databox::client() %>% 
  add_metric("sales", 83000, Sys.Date()) %>% 
  add_metric("sales", 4000, unit="USD") %>% 
  add_metric("expenses", 87500) %>% 
  add_metric("sales", 123000, mattrs=c("channel"="in-person", "cheese"="manchego")) %>% 
  print()
```

Also can validate the last push:

```{r}
glimpse(last_push())
```

### Test Results

```{r message=FALSE}
library(databox)
library(testthat)

date()

test_dir("tests/")
```
